Testing traversability of protein tunnels with flexible ligands using motion planning

### 2017-06-08 paper.tex
ml-rrt refs + atom metric

\def\C{\mathcal{C}}
\def\CF{\mathcal{C}_{free}}
\def\CFD{{\mathcal{C}^s_{free}}}
\def\dt{d_{goal}}

@@

\def\VV{V_{vor}}
\def\VVA{V_{vor}^{act}}
\def\da{d_{high}}
\def\db{d_{low}}

@@

The most related work to this paper is the MoMa-LigPath~\cite{cortes2005path}, that is based on the ML-RRT method~\cite{cortes2010simulating}.
In comparison to our solution, the method~\cite{cortes2005path} aims for find any path leading towards the active site without
possibility to select a tunnel of interest.

@@

\begin{algorithm}[h]
%\setstretch{\straa}
\caption{\label{alg::expand}expand}
\KwIn{
   configuration $\qnear$ to be expanded,
}
\KwData{
   ligand conformations $\L$,
   scale limits $\smin, \smax$ and $\sdelta$
}
%\KwOut{
%    set $S$ of collision-free configurations reachable from $\qnear$\;
%}
\hrule
\ForEach{$l \in \L$}{
%    $newnodes = $ false\;
    \ForEach{$s \in (\smax,\smax-\sdelta, \ldots, \smin)$}{
        \For{$i = 1,\ldots,m$}{
            $q' = q$\;
            translate $q$ by random around $q'$\;
            rotate randomly \;
            $q'.l = l$\;
            $q'.s = s$\;
            $qn$ = nearest node in $\T$ towards $q'$\;
            \If{$isCollisionFree(q')$ {\bf and} $d(q',\qnear) < d(q',qn)$}{
                $\T$.addNode($q$)\;
                $\T$.addEdge($\qnear,q$)\;
%                $S = S \cup \{ q \}$\;
%                $newnodes = $ true\;
                {\bf break}\;
            }
        }
    }
}
%\return $S$\;
\end{algorithm}

>>>>

\def\C{\mathcal{C}}
\def\CF{\mathcal{C}_{free}}
\def\CFD{{\mathcal{C}^s_{free}}}
\def\dt{d_{goal}}
\def\da{d_{atom}}

@@

\def\VV{V_{vor}}
\def\VVA{V_{vor}^{act}}

@@

The most related work to this paper is the MoMa-LigPath~\cite{cortes2005path}, that is based on the ML-RRT method~\cite{cortes2010simulating,cortes2007mlrrt}.
In comparison to our solution, the method~\cite{cortes2005path} aims for find any path leading towards the active site without
possibility to select a tunnel of interest.

@@

todo atom metric

\begin{algorithm}[h]
%\setstretch{\straa}
\caption{\label{alg::expand}expand}
\KwIn{
   configuration $\qnear$ to be expanded,
}
\KwData{
   ligand conformations $\L$,
   scale limits $\smin, \smax$ and $\sdelta$
}
%\KwOut{
%    set $S$ of collision-free configurations reachable from $\qnear$\;
%}
\hrule
\ForEach{$l \in \L$}{
%    $newnodes = $ false\;
    \ForEach{$s \in (\smax,\smax-\sdelta, \ldots, \smin)$}{
        $\qnew = \emptyset$; // empty configuration\\
        \For{$i = 1,\ldots,m$}{
            $q=\qnear$\;
            $q.position$ = random 3D position around $\qnear$\;
            $q.rotation$ = random 3D rotation\;
            $q.l = l$\; 
            $q.s = s$\;
            \If{isCollisionFree($q$) {\bf and} \\ $(\qnew = \emptyset$ {\bf or} $\da(q, \qnear) < \da(\qnew,\qnear))$} {
                $\qnew = q$\;
            } 
        }
        $\T$.addNode($q$)\;
        $\T$.addEdge($\qnear,q$)\;
    }
}
%\return $S$\;
\end{algorithm}
